\documentclass[titlepage]{article}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{graphicx}

\title{CS 440 - Homework 7}
\author{Matthew Liu}
\date{}

\begin{document}
\maketitle{}

\noindent \textbf{1. } Conceptual Questions \\

\begin{enumerate}
	\item What is the example space, \textbf{\textit{X}}, for this problem?
	\item Which model do you expect to be more expressive: a binary classifier perceptron or a binary classifier multi-layer perceptron with one hidden layer? Why?
	\item Which one of the models described in question 2 do you think is more likely to overfit, and why?
	\item Do you expect your perceptron to converge (assuming a constant learning rate)? Why or why not?
\end{enumerate}

\noindent \textbf{2. } Implementing a Perceptron \\

\begin{enumerate}
	\item Try adjusting each setting listed above, and report which combination (learning rate, training example ordering, and weight initialization) worked best. If you used random initial weights, specify what distribution the weights came from (uniform, Gaussian, or another distribution).
	\item How many epochs were necessary to train your perceptron?
	\item What accuracy did you achieve on the training set?
	\item What accuracy did you achieve on the test set?	
\end{enumerate}

\noindent \textbf{2. } Using a Multilayer Perceptron \\

\begin{enumerate}
	\item Which combinations of hyperparameters did you try, and which combination worked best?
	\item How many epochs were necessary to train your multilayer perceptron?
	\item What accuracy did you achieve on the training set?
	\item What accuracy did you achieve on the test set?	
	\item How did the results obtained using the multilayer perceptron compare to those obtained using the single-layer perceptron in part 2? Explain the differences.
\end{enumerate}

\end{document}